Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-09-02 bbbq_article.tex
Nice table of software

\begin{table}[]
  \begin{tabular}{lll}
    Goal & Tool  \\ 
    \hline
    Predict topology                  & TMHMM \cite{krogh2001predicting} \\
    Predict topology                  & PureseqTM \cite{wang2019efficient} \\
    Predict epitopes MHC-I            & \verb;epitope-prediction; \cite{bianchi2017} \\
    Predict epitopes MHC-II           & NetMHCIIpan \cite{nielsen2008quantitative,karosiene2013netmhciipan} \\
    Predict epitopes MHC-I and MHC-II & MHCnuggets \cite{shao2020high} \\
    Call TMHMM from R                 & tmhmm \cite{tmhmm} \\
    Call PureseqTM from R             & pureseqtmr \cite{pureseqtmr} \\
    Call NetMHCIIpan from R           & netmhc2pan \cite{netmhc2pan} \\
    Call MHCnuggets from R            & mhcnuggetsr \cite{mhcnuggetsr} \\
    \verb;epitope-prediction; LUT     & epiprepreds \cite{epiprepreds} \\
    NetMHCIIpan LUT                   & nmhc2ppreds \cite{nmhc2ppreds} \\
    MHCnuggets LUT                    & mhcnpreds \cite{mhcnpreds} \\
    Combine all                       & bbbq \cite{bbbq}
  \end{tabular}
  \caption{
    Overview of all software used in this research.
    Software without a reference is written for this research.
    'LUT' is an abbreviation for 'Look-up table'. 
  }
  \label{table:software_used}
\end{table}

>>>>

\begin{table}[]
  \begin{tabular}{llll}
    Goal & Tool & Reference \\ 
    \hline
    Predict topology                  & TMHMM                     & \cite{krogh2001predicting} \\
    Predict topology                  & PureseqTM                 & \cite{wang2019efficient} \\
    Predict epitopes MHC-I            & \verb;epitope-prediction; & \cite{bianchi2017} \\
    Predict epitopes MHC-II           & NetMHCIIpan               & \cite{nielsen2008quantitative,karosiene2013netmhciipan} \\
    Predict epitopes MHC-I and MHC-II & MHCnuggets                & \cite{shao2020high} \\
    Call TMHMM from R                 & tmhmm                     & \cite{tmhmm} \\
    Call PureseqTM from R             & pureseqtmr                & \cite{pureseqtmr} \\
    Call NetMHCIIpan from R           & netmhc2pan                & \cite{netmhc2pan} \\
    Call MHCnuggets from R            & mhcnuggetsr               & \cite{mhcnuggetsr} \\
    \verb;epitope-prediction; LUT     & epiprepreds               & \cite{epiprepreds} \\
    NetMHCIIpan LUT                   & nmhc2ppreds               & \cite{nmhc2ppreds} \\
    MHCnuggets LUT                    & mhcnpreds                 & \cite{mhcnpreds} \\
    Sequence alignment                & ClustalW                  & \cite{thompson1994clustal} \\
    Conservation scores               & msa                       & \cite{bodenhofer2015msa} \\
    Combine all                       & bbbq                      & \cite{bbbq}
  \end{tabular}
  \caption{
    Overview of all software used in this research.
    'LUT' is an abbreviation for 'Look-up table'. 
  }
  \label{table:software_used}
\end{table}
